Using Path-Dependent Types to Build Type Safe JavaScript Foreign Function Interfaces

### 2014-04-07 papers/icwe14/icwe14.tex
minor rewording

We observe that, despite these languages are statically typed, their integration of the browser API either is not type safe or over constrain the programmers. Indeed, integrating an API designed for a dynamically typed language into a statically typed language can be challenging. For instance, the \jscode{createElement} function return type depends on the value of its parameter: \jscode{createElement('div')} returns a \jscode{DivElement}, \jscode{createElement('input')} returns an \jscode{InputElement}, \emph{etc}.

@@

Sebastien Doreane proposed a way to integrate JavaScript APIs in Scala~\cite{Doeraene13_ScalaJs}. His approach allows developers to seamlessly use JavaScript APIs from statically typed Scala code. However, he did not use the features of Scala's type system, as we did, to leverage more precise types when possible.

>>>>

We observe that, even though these languages are statically typed, their integration of the browser API either is not type safe or over constrain the programmers. Indeed, integrating an API designed for a dynamically typed language into a statically typed language can be challenging. For instance, the \jscode{createElement} function return type depends on the value of its parameter: \jscode{createElement('div')} returns a \jscode{DivElement}, \jscode{createElement('input')} returns an \jscode{InputElement}, \emph{etc}.

@@

Sebastien Doreane proposed a way to integrate JavaScript APIs in Scala~\cite{Doeraene13_ScalaJs}. His approach allows developers to seamlessly use JavaScript APIs from statically typed Scala code. However, his work does not expose types as precise as ours (\emph{e.g.} in their encoding the return type of \jscode{createElement} is always \jscode{Element}).
